cardinalR: Generating interesting high-dimensional data structures

### 2025-08-22 paper-cardinalR.Rmd
Added Scurve data

```{r, eval=FALSE}
langevitour::langevitour(scurve)
```

@@

```{r, eval=FALSE}
langevitour::langevitour(scurvehole)
```

@@

```{r, label = "fig-scurve-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `scurve` (a1-a3) and `scurvehole` (b1-b3) data.", fig.width=15, fig.height=10}

>>>>

```{r}
scurve_lang <- langevitour::langevitour(scurve, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r}
scurvehole_lang <- langevitour::langevitour(scurvehole, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r scurve, eval=knitr::is_html_output(), fig.cap="`langevitour` output  of the `scurve` data in $4\\text{-}D$."}

scurvefig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr;",
    scurve_lang, scurvehole_lang
  ),
  device = "xs"
)

class(scurvefig) <- c(class(scurvefig), "htmlwidget")

scurvefig
```

```{r scurve-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `scurve` (a1-a3) and `scurvehole` (b1-b3) data.", fig.width=15, fig.height=10}

### 2025-08-22 paper-cardinalR.tex
Added Scurve data

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-scurve-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `scurve` (a1-a3) and `scurvehole` (b1-b3) data.}\label{fig:fig-scurve-proj}
\end{figure}

>>>>

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/scurve-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `scurve` (a1-a3) and `scurvehole` (b1-b3) data.}\label{fig:scurve-proj}
\end{figure}
